---
title: "FactorReport2"
author: "MarkHE"
date: "Sunday, September 20, 2015"
output: pdf_document
---

First,let's point out the colinearity inside factors. 
```{r,cache=TRUE,echo=FALSE}
load("C:/Users/shixi19/Desktop/data_for_part2.RData")
cordata<-data.frame(beta=betagain,momentum=momentumgain,size=sizegain,value=valuegain,vol=volatilitygain,growth=growthgain,exp=expectationgain,leverage=leveragegain,news=newsgain)
cor(cordata)
```

Read in Data

```{r,cache=TRUE,warning=TRUE,echo=FALSE,comment="",results='hide'}
#Preparation#
#=============================================================================#
{
setwd("C:\\Users\\shixi19\\Desktop\\RFactorModel")
library(WindR)
w.start(showmenu=F)
#options(warn=-1)
}
```

```{r,cache=TRUE,warning=TRUE,echo=FALSE,comment=""}
#=============================================================================#
#Public functions#
{
savedata<-function(x){
      write.csv(get(x),file=paste0("C:\\Users\\shixi19\\Desktop\\FactorData2\\",x,".csv"))
}##give the name of the variable as a character 
readdata<-function(x){
      data<-read.csv(file=paste0("C:\\Users\\shixi19\\Desktop\\FactorData2\\",x,".csv"))
      data<-data[,-1]
      names(data)<-substr(names(data),2,10)
      return(data)
}##give the name of the variable as a character 
startdatefun<-function(y){
year<-substr(Sys.Date(),1,4)
year<-as.numeric(year)
year<-year-y
year<-as.character(year)
startdate<-paste0(year,"0101")
startdate}
startdatefunwithhash<-function(y){
year<-substr(Sys.Date(),1,4)
year<-as.numeric(year)
year<-year-y
year<-as.character(year)
startdate<-paste0(year,"-01-01")
return(startdate)}
startdatefunwithnohash<-function(y){
      year<-substr(Sys.Date(),1,4)
      year<-as.numeric(year)
      year<-year-y
      year<-as.character(year)
      startdate<-paste0(year,"0101")
      return(startdate)}
#Read in all A stocks at the time of startdate and follow the industry 
#classification of citic 
stocklistfun<-function(y){
      startdate<-startdatefun(y)
#       stocklist<-w.wset('SectorConstituent',
#                         paste0('date=',startdate,';sectorId=a001010100000000'))
#      stocklist<-w.wset('SectorConstituent',
#                        paste0('date=',startdate,';windcode=000300.SH'))
        stocklist<-w.wset('SectorConstituent',
                          paste0('date=',startdate,';windcode=000906.SH'))
      stock<-stocklist$Data$wind_code#Get the code for all A stock
      stockname<-stocklist$Data$sec_name#Get the name for all A stock
      industrycode<-w.wss(stock,'industry_citiccode,industry_citic',
        paste0('tradeDate=',startdate),'industryType=1')$Data$INDUSTRY_CITICCODE
      industryname<-w.wss(stock,'industry_citiccode,industry_citic',
        paste0('tradeDate=',startdate),'industryType=1')$Data$INDUSTRY_CITIC
      stock_industry<-rbind(stock,industrycode,industryname)
      stock_industry<-stock_industry[,stock_industry[3,]!="NaN"]
      stock_industry
}#Change the initial stock pool here!#
removeNA<-function(data){
      data[is.na(data)]=0
      data
}
standard<-function(data){
      getmid<-apply(data[,-1],1,median,na.rm=TRUE)
      getmid<-removeNA(getmid)#Since we have set apply function as na.rm=TRUE,Here we can let         
      #na equals zero because they must come from those row with straight NA
      middistance<-abs(data[,-1]-getmid)
      mid<-apply(middistance,1,median,na.rm=TRUE)
      mid<-removeNA(mid)
      data1<-data[,-1]
      data1<-removeNA(data1)
      for(i in 1:length(getmid)){
            
            data1[i,data1[i,]-getmid[i]>3*abs(mid[i])]<-getmid[i]+3*abs(mid[i])
            data1[i,data1[i,]-getmid[i]<(-3*abs(mid[i]))]<-getmid[i]+(-3*abs(mid[i]))
            
      }
      data[,-1]<-data1
       getmean<-apply(data[,-1],1,mean,na.rm=TRUE)
      getmean<-removeNA(getmean)
      data[,-1]<-data[,-1]-getmean
      getvar<-apply(data[,-1],1,var,na.rm=TRUE)
      getvar[is.na(getvar)]<-1
      getvar[getvar==0]<-1
      data[,-1]<-data[,-1]/sqrt(getvar)
      data
}
standard_m<-function(data){##No standard only remove extremes
      getmid<-apply(data[,-1],1,median,na.rm=TRUE)
      getmid<-removeNA(getmid)#Since we have set apply function as na.rm=TRUE,Here we can let         
      #na equals zero because they must come from those row with straight NA
      middistance<-abs(data[,-1]-getmid)
      mid<-apply(middistance,1,median,na.rm=TRUE)
      mid<-removeNA(mid)
      data1<-data[,-1]
      data1<-removeNA(data1)
      for(i in 1:length(getmid)){
            
            data1[i,data1[i,]-getmid[i]>3*abs(mid[i])]<-getmid[i]+3*abs(mid[i])
            data1[i,data1[i,]-getmid[i]<(-3*abs(mid[i]))]<-getmid[i]+(-3*abs(mid[i]))
            
      }
      data[,-1]<-data1
      data
}
RemoveNA<-function(x){
      x<-x[,-1]
      x[is.na(x)]<-0
      x
}
sizeweight<-function(stocklist){
      weight<-w.wss(stocklist,'total_shares',paste0('tradeDate=',Sys.Date()))$Data$TOTAL_SHARES
      tot<-sum(weight)
      weight<-weight/tot
      weight
}
}
```

```{r,cache=TRUE,warning=TRUE,echo=FALSE,comment=""}
#Determine the public variables#
#=============================================================================#
y<-2
#This indicates how many years to look back which has to be less than 10
#Strongly suggest to set y<-2 since the data of expected level are available
#since 2013
#-----------------------------------------------------------------------------#
stock_industry<-stocklistfun(y)
stocklist<-stock_industry[1,]#Use it too often so that I list it seperately
num.industry<-as.numeric(length(unique(stock_industry[3,])))
num.stock<-as.numeric(length(stock_industry[1,]))
#checkdate<-datepoint(y)
savedata("stocklist")
sizeweight_l<-sizeweight(stocklist)
#=============================================================================#
```

```{r,cache=TRUE,warning=TRUE,echo=FALSE,comment=""}
#=============================================================================#
#Functions to use#
{
# stockperform250day<-function(stocklist,checkdate){
#       data<-w.wsd(stocklist,"pct_chg","ED-250D",
#             checkdate,"Fill=Previous;PriceAdj=F")$Data
#       data<-removeNA(data)
#       data
# }
# indexperform250day<-function(indexname,checkdate){
#       data<-w.wsd(as.character(indexname),"pct_chg","ED-250D",checkdate
#             ,"Fill=Previous;PriceAdj=F")$Data
#       data<-removeNA(data)
#       data
#}#indexname:"000300.SH"or"000906.SH"
weight<-function(num,groupnum){
      weight<-rep(1:groupnum,each=ceiling(num/groupnum))
      weight<-weight[1:num]
      sum<-sum(weight)
      weight<-weight/sum
      weight
}
# stockperformance<-stockperform250day(stocklist,checkdate)
# indexperformance<-indexperformance250day("000300.SH",checkdate)

#Gain#
gainf<-function(y,stocklist){
      data<-w.wsd(stocklist,"pct_chg",startdatefunwithhash(y),Sys.Date()
            ,"Fill=Previous;PriceAdj=F")$Data
      data[,-1]<-data[,-1]/100
      data<-removeNA(data)
      data
}
#Beta#
betafun<-function(y,stocklist){
      data<-w.wsd(stocklist,"beta_100w",startdatefunwithhash(y),Sys.Date()
            ,"Fill=Previous;PriceAdj=F")$Data
#       print(paste0("beta missing value:",sum(is.na(data)),"/",nrow(data)*ncol(data)))
      data<-standard(data)
      data<-removeNA(data)
      data
}
#Momentum#
momentumfun<-function(y,stocklist){
      data<-w.wsd(stocklist,"annualyeild_100w",startdatefunwithhash(y),Sys.Date()
            ,"Fill=Previous;PriceAdj=F")$Data
#       print(paste0("momentum missing value:",sum(is.na(data)),"/",nrow(data)*ncol(data)))
      data[,-1]<-data[,-1]/100
      data<-standard(data)
      data<-removeNA(data)
      data
}
#Size#
sizefun<-function(y,stocklist){
      data<-w.wsd(stocklist,"total_shares",startdatefunwithhash(y),Sys.Date(),
            "Fill=Previous;PriceAdj=F")$Data
#       print(paste0("size missing value:",sum(is.na(data)),"/",nrow(data)*ncol(data)))
      data<-removeNA(data)
      data[,-1]<-log10(data[,-1])
      data<-standard(data)
      data<-removeNA(data)
      data
}
#Earnings Yield#
eroefun<-function(y,stocklist){
      data<-w.wsd(stocklist,"west_avgroe_FY1",startdatefunwithhash(y),Sys.Date(),
                  "Fill=Previous;PriceAdj=F")$Data
#       print(paste0("eroe missing value:",sum(is.na(data)),"/",nrow(data)*ncol(data)))
      data<-standard(data)
      data<-removeNA(data)
      data
}
eepsfun<-function(y,stocklist){
      data<-w.wsd(stocklist,"west_eps_FY1",startdatefunwithhash(y),Sys.Date(),
                  "Fill=Previous;PriceAdj=F")$Data
#       print(paste0("eeps missing value:",sum(is.na(data)),"/",nrow(data)*ncol(data)))
      data<-standard(data)
      data<-removeNA(data)
      data
}
pefun<-function(y,stocklist){
      data<-w.wsd(stocklist,"rating_avg",startdatefunwithhash(y),Sys.Date(),
                  "Fill=Previous;PriceAdj=F")$Data
#        print(paste0("pe missing value:",sum(is.na(data)),"/",nrow(data)*ncol(data)))
      data<-standard(data)
      data<-removeNA(data)
      data
}

}
```

```{r,cache=TRUE,warning=TRUE,echo=FALSE,comment=""}
#Read in Data#
#Performance#
{
gain<-gainf(y,stocklist)
}
savedata("gain")
#Beta#
{
      beta<-betafun(y,stocklist)
}
savedata("beta")
#Momentum#
{
momentum<-momentumfun(y,stocklist)
}
savedata("momentum")
#Size#
{
size<-sizefun(y,stocklist)
}
savedata("size")
#Expectation#
{
#Read in sub factors#
{
eroe<-eroefun(y,stocklist)
eeps<-eepsfun(y,stocklist)
pe<-pefun(y,stocklist)
}
}
savedata("eroe")
savedata("eeps")
savedata("pe")
{#Optimization#
{
calgain<-function(variables,eroe,eeps,pe){
  gain=eroe
  gain[,-1]=variables[1]*(eroe[,-1])+variables[2]*(eeps[,-1])+variables[3]*(pe[,-1])
  gain<-removeNA(gain)
  gain
}

difference<-function(variables,eroe,eeps,pe,real){
      diff<-sum(((real[,-1])-calgain(variables,eroe,eeps,pe)[,-1])^2)
      diff<-removeNA(diff)
      diff
}
variables<-c(1,1,1)
optimresult<-optim(variables,difference,eroe=eroe[-nrow(eroe),],
                   eeps=eeps[-nrow(eeps),],pe=pe[-nrow(pe),],real=gain[-1,])
subweight<-optimresult$par
}
#Generate Earnings Yield#
earningsyield<-calgain(subweight,eroe,eeps,pe)
earningsyield<-standard(earningsyield)
expectation<-earningsyield
}
savedata("expectation")

```


```{r,cache=TRUE,warning=TRUE,echo=FALSE,comment=""}
#!Change the base index here!##There is another at the latter part!#
{
      zcf1_CLOSE_p<-w.wsd("000906.SH","pct_chg",startdatefunwithhash(y),
                          Sys.Date(),"Fill=Previous;PriceAdj=F")$Data$PCT_CHG
       zcf1_CLOSE_p_m<-w.wsd("000906.SH","pct_chg",startdatefunwithhash(y),
                          Sys.Date(),"Period=M;Fill=Previous;PriceAdj=F")$Data$PCT_CHG
}
savedata("zcf1_CLOSE_p")
```
# I have put the month and week date here! But how to use...
```{r,cache=TRUE,warning=TRUE,echo=FALSE,comment=""}
data<-w.wsd(stocklist,"pct_chg",startdatefunwithhash(y),Sys.Date(),"Period=M;Fill=Previous;PriceAdj=F")$Data
data[,-1]<-data[,-1]/100
monthgain<-removeNA(data)
monthdate<-monthgain[,1]
data<-w.wsd(stocklist,"pct_chg",startdatefunwithhash(y),Sys.Date(),"Period=W;Fill=Previous;PriceAdj=F")$Data
data[,-1]<-data[,-1]/100
weekgain<-removeNA(data)
weekdate<-weekgain[,1]
plotdate<-beta[,1]
```

#Monthly data
```{r,cache=TRUE,warning=TRUE,echo=FALSE,comment=""}
#Gain#
gainf_m<-function(y,stocklist){
      data<-w.wsd(stocklist,"pct_chg",startdatefunwithhash(y),Sys.Date()
            ,"Period=M;Fill=Previous;PriceAdj=F")$Data
      data[,-1]<-data[,-1]/100
      data<-removeNA(data)
      data
}
#Beta#
betafun_m<-function(y,stocklist){
      data<-w.wsd(stocklist,"beta_100w",startdatefunwithhash(y),Sys.Date()
            ,"Period=M;Fill=Previous;PriceAdj=F")$Data
#       print(paste0("beta missing value:",sum(is.na(data)),"/",nrow(data)*ncol(data)))
      data<-standard_m(data)
      data<-removeNA(data)
      data
}
#Momentum#
momentumfun_m<-function(y,stocklist){
      data<-w.wsd(stocklist,"annualyeild_100w",startdatefunwithhash(y),Sys.Date()
            ,"Period=M;Fill=Previous;PriceAdj=F")$Data
#       print(paste0("momentum missing value:",sum(is.na(data)),"/",nrow(data)*ncol(data)))
      data[,-1]<-data[,-1]/100
      data<-standard_m(data)
      data<-removeNA(data)
      data
}
#Size#
sizefun_m<-function(y,stocklist){
      data<-w.wsd(stocklist,"total_shares",startdatefunwithhash(y),Sys.Date(),
            "Period=M;Fill=Previous;PriceAdj=F")$Data
#       print(paste0("size missing value:",sum(is.na(data)),"/",nrow(data)*ncol(data)))
      data<-removeNA(data)
      data[,-1]<-log10(data[,-1])
      data<-standard_m(data)
      data<-removeNA(data)
      data
}
#Earnings Yield#
eroefun_m<-function(y,stocklist){
      data<-w.wsd(stocklist,"west_avgroe_FY1",startdatefunwithhash(y),Sys.Date(),
                  "Period=M;Fill=Previous;PriceAdj=F")$Data
#       print(paste0("eroe missing value:",sum(is.na(data)),"/",nrow(data)*ncol(data)))
      data<-standard_m(data)
      data<-removeNA(data)
      data
}
eepsfun_m<-function(y,stocklist){
      data<-w.wsd(stocklist,"west_eps_FY1",startdatefunwithhash(y),Sys.Date(),
                  "Period=M;Fill=Previous;PriceAdj=F")$Data
#       print(paste0("eeps missing value:",sum(is.na(data)),"/",nrow(data)*ncol(data)))
      data<-standard_m(data)
      data<-removeNA(data)
      data
}
pefun_m<-function(y,stocklist){
      data<-w.wsd(stocklist,"rating_avg",startdatefunwithhash(y),Sys.Date(),
                  "Period=M;Fill=Previous;PriceAdj=F")$Data
#        print(paste0("pe missing value:",sum(is.na(data)),"/",nrow(data)*ncol(data)))
      data<-standard_m(data)
      data<-removeNA(data)
      data
}
#Read in Data#
#Performance#
{
gain_m<-gainf_m(y,stocklist)
}
#Beta#
{
beta_m<-betafun_m(y,stocklist)
}
#Momentum#
{
momentum_m<-momentumfun_m(y,stocklist)
}
#Size#
{
size_m<-sizefun_m(y,stocklist)
}
#Expectation
{
#Read in sub factors#
{
eroe_m<-eroefun_m(y,stocklist)
eeps_m<-eepsfun_m(y,stocklist)
pe_m<-pefun_m(y,stocklist)
}
}
{#Optimization#
{
calgain<-function(variables,eroe,eeps,pe){
  gain=eroe
  gain[,-1]=variables[1]*(eroe[,-1])+variables[2]*(eeps[,-1])+variables[3]*(pe[,-1])
  gain<-removeNA(gain)
  gain
}

difference<-function(variables,eroe,eeps,pe,real){
      diff<-sum(((real[,-1])-calgain(variables,eroe,eeps,pe)[,-1])^2)
      diff<-removeNA(diff)
      diff
}
variables<-c(1,1,1)
optimresult<-optim(variables,difference,eroe=eroe_m[-nrow(eroe_m),],
                   eeps=eeps_m[-nrow(eeps_m),],pe=pe_m[-nrow(pe_m),],real=gain_m[-1,])
subweight<-optimresult$par
}
#Generate Earnings Yield#
earningsyield<-calgain(subweight,eroe_m,eeps_m,pe_m)
earningsyield_m<-standard_m(earningsyield)
expectation_m<-earningsyield_m
}



```

```{r}
sizeweight_l<-sizeweight(stocklist)
savedata("sizeweight_l")
```

```{r}
save.image("C:/Users/shixi19/Desktop/FactorReport2_1.RData")
```

Read in Over
# This chunk must be executed before porto decision
```{r}
regplot<-function(i){
regdatafun<-function(i){
      regdata<-data.frame(extragain=as.numeric(gain[i+1,-1])-(as.numeric(zcf1_CLOSE_p[i+1])/100),
                          beta=as.numeric(beta[i,-1]),
                          momentum=as.numeric(momentum[i,-1]),
                          size=as.numeric(size[i,-1]),
                          expectation=as.numeric(expectation[i,-1])
      ,indus=factor(as.character(stock_industry[3,])))
      return(regdata)
}
regdata<-regdatafun(i)
full.model<-lm(extragain~.,data=regdata)
# best.model<-step(full.model,direction="backward")
# par(mfrow=c(2,2),mar=c(2,4,2,2))
# plot(full.model)
return(summary(full.model))
}
```


# This chunk must be executed before porto decision
```{r}
residualgain<-matrix(0,(nrow(beta)-1),(ncol(beta)-1))
{
      t<-regplot(1)
      betagain<-t$coefficients[1,1]
      momentumgain<-t$coefficients[2,1]
      sizegain<-t$coefficients[3,1]
      expectationgain<-t$coefficients[4,1]
      residualgain[1,]<-t$residuals
      
      betat<-t$coefficients[1,3]
      momentumt<-t$coefficients[2,3]
      sizet<-t$coefficients[3,3]
      expectationt<-t$coefficients[4,3]
      
}
for(i in 2:(nrow(beta)-1)){
      t<-regplot(i)
      betagain<-c(betagain,t$coefficients[1,1])
      momentumgain<-c(momentumgain,t$coefficients[2,1])
      sizegain<-c(sizegain,t$coefficients[3,1])
      expectationgain<-c(expectationgain,t$coefficients[4,1])
      residualgain[i,]<-t$residuals
      
      betat<-c(betat,t$coefficients[1,3])
      momentumt<-c(momentumt,t$coefficients[2,3])
      sizet<-c(sizet,t$coefficients[3,3])
      expectationt<-c(expectationt,t$coefficients[4,3])
}
cordata<-data.frame(beta=betagain,momentum=momentumgain,size=sizegain,exp=expectationgain)
cor(cordata)
```
calculate the risk
```{r}
covmatrix<-cov(cordata)

```
#Decide the changing porto date,not used by far,used after get porto weight
```{r}
factor_actual<-matrix(0,(nrow(growth)-4),4)
 factor_actual[i,]<-inequalcon_real(testmulti_final[i,])#actual beta
```

just test the porto for the first time
```{r}

temp<-rbind(sizeweight_l,stock_industry)
indusweight<-temp

library(parallel)
library(foreach)
library(doParallel)
library(truncnorm)
library(Rsolnp)

tindex<-as.numeric(tapply(as.numeric(indusweight[1,]),as.character(indusweight[4,]),sum))
getporto_final<-function(i){
      library(truncnorm)
      library(Rsolnp)
         gainfun<-function(w){
               if(i==3){
                     startdate_risk<-plotdate[1]
               }else{
                     startdate_risk<-monthdate[i-3]
               }
            -(as.numeric(0.2*w%*%as.numeric(gain_m[i-2,-1])+0.3*w%*%as.numeric(gain_m[i-1,-1])+0.5*w%*%as.numeric(gain_m[i,-1]))-(0.5*zcf1_CLOSE_p_m[i]/100+0.3*zcf1_CLOSE_p_m[i-1]/100+0.2*zcf1_CLOSE_p_m[i-2]/100))+7.5*getrisk(startdate_risk,monthdate[i],w)#Lambda=7.5
      }
      equalcon<-function(w){
           sum(w)
      }
      inequalcon<-function(w){
            a<-0.5*((as.numeric((w-sizeweight_l)%*%as.numeric(beta_m[i,-1])))/(sqrt(sizeweight_l%*%(as.numeric(beta_m[i,-1])^2))))+0.3*((as.numeric((w-sizeweight_l)%*%as.numeric(beta_m[i-1,-1])))/(sqrt(sizeweight_l%*%(as.numeric(beta_m[i-1,-1])^2))))+0.2*((as.numeric((w-sizeweight_l)%*%as.numeric(beta_m[i-2,-1])))/(sqrt(sizeweight_l%*%(as.numeric(beta_m[i-2,-1])^2))))
            b<-0.5*((as.numeric((w-sizeweight_l)%*%as.numeric(momentum_m[i,-1])))/(sqrt(sizeweight_l%*%(as.numeric(momentum_m[i,-1])^2))))+0.3*((as.numeric((w-sizeweight_l)%*%as.numeric(momentum_m[i-1,-1])))/(sqrt(sizeweight_l%*%(as.numeric(momentum_m[i-1,-1])^2))))+0.2*((as.numeric((w-sizeweight_l)%*%as.numeric(momentum_m[i-2,-1])))/(sqrt(sizeweight_l%*%(as.numeric(momentum_m[i-2,-1])^2))))
            c<-0.5*((as.numeric((w-sizeweight_l)%*%as.numeric(size_m[i,-1])))/(sqrt(sizeweight_l%*%(as.numeric(size_m[i,-1])^2))))+0.3*((as.numeric((w-sizeweight_l)%*%as.numeric(size_m[i-1,-1])))/(sqrt(sizeweight_l%*%(as.numeric(size_m[i-1,-1])^2))))+0.2*((as.numeric((w-sizeweight_l)%*%as.numeric(size_m[i-2,-1])))/(sqrt(sizeweight_l%*%(as.numeric(size_m[i-2,-1])^2))))
            d<-0.5*((as.numeric((w-sizeweight_l)%*%as.numeric(earningsyield_m[i,-1])))/(sqrt(sizeweight_l%*%(as.numeric(earningsyield_m[i,-1])^2))))+0.3*((as.numeric((w-sizeweight_l)%*%as.numeric(earningsyield_m[i-1,-1])))/(sqrt(sizeweight_l%*%(as.numeric(earningsyield_m[i-1,-1])^2))))+0.2*((as.numeric((w-sizeweight_l)%*%as.numeric(earningsyield_m[i-2,-1])))/(sqrt(sizeweight_l%*%(as.numeric(earningsyield_m[i-2,-1])^2))))
            
            a<-removeNA(a)
            b<-removeNA(b)
            c<-removeNA(c)
            d<-removeNA(d)
#             tt<-rbind(as.numeric(w),indusweight[4,])
#             treal<-as.numeric(tapply(as.numeric(tt[1,]),as.character(tt[2,]),sum))
#             v2<-sum(abs(treal-tindex))/2
#             return(c(a,b,c,d,v2))
            return(c(a,b,c,d))
      }
      portofolio<-solnp(pars=sizeweight_l,fun=gainfun
                        ,eqfun=equalcon,eqB=1,ineqfun=inequalcon
                        ,ineqLB=(c(-0.1,-0.1,-0.1,-1))
                        ,ineqUB=(c(0.1,0.1,0.1,1)),
                        LB=rep(0,num.stock),UB=rep(0.1,num.stock))##Means we cannot put more than 10 percent weight on one single stock  
write.csv(portofolio$par,file=paste0("C:\\Users\\shixi19\\Desktop\\FactorData2\\",as.character(i),".csv"))#leave some track after each time
      return(portofolio$par)
}
cl <- makeCluster(4)
registerDoParallel(cl)
#testmulti_final<- foreach(x=3:33,.combine='rbind') %dopar% getporto_final(x)
#31 failed!
testmulti_final<- foreach(x=3:30,.combine='rbind') %dopar% getporto_final(x)
stopCluster(cl)


library(ggplot2)
lookback<-function(w){
      n<-nrow(w)
      performance<-matrix(1,n+1,1)
      for(i in 1:n){
            w1<-w[i,]
            performance[i+1]<-performance[i]*(1+w1%*%as.numeric(gain_m[i+3,-1])-zcf1_CLOSE_p_m[i+3]/100)
      }
      x<-size_m[3:(n+3),1]
      qplot(x,performance,geom="line")
}
lookback(testmulti_final)
```


#risk model is here!
```{r}
##Use the EWMA method(page 13 of 37 on the gtja report)
lambda<-function(tao){
      lambda<-0.5^(1/tao)
      return(lambda)
}
# CalCov<-function(d1,d2){
#       i1<-grep(d1,plotdate)
#       i2<-grep(d2,plotdate)
#       tempbeta<-betagain[i1:i2]
#       tempmom<-momentumgain[i1:i2]
#       tempsize<-sizegain[i1:i2]
#       tempexp<-expectationgain[i1:i2]
#       abeta<-mean(tempbeta)
#       amom<-mean(tempmom)
#       asize<-mean(tempsize)
#       aexp<-mean(tempexp)
#       sumfenzi<-0
#       sumfenmu<-0
#       for(i in 1:as.numeric(d2-d1)){
#             sumfenzi<-sumfenzi+lambda(as.numeric(d2-d1)-i+1)*(tempbeta[i]-abeta)
#       }
# }
getdatareadyforcov<-function(d1,d2){
      i1<-grep(d1,plotdate)
      i2<-grep(d2,plotdate)
      tempbeta<-betagain[i1:i2]
      tempmom<-momentumgain[i1:i2]
      tempsize<-sizegain[i1:i2]
      tempexp<-expectationgain[i1:i2]
      covdata<-data.frame(beta=tempbeta,momentum=tempmom,size=tempsize,expectation=tempexp)
      return(covdata)
}
getrisk<-function(d1,d2,w){
i1<-grep(d1,plotdate)
i2<-grep(d2,plotdate)
      #Common Risk
covf<-cov(getdatareadyforcov(d1,d2))
covf<-rbind(as.numeric(covf[1,]),as.numeric(covf[2,]),as.numeric(covf[3,]),as.numeric(covf[4,]))
x<-rbind(as.numeric(beta[i2,-1]),as.numeric(momentum[i2,-1]),as.numeric(size[i2,-1]),as.numeric(expectation[i2,-1]))
#Special risk
tempresidual<-residualgain[i1:i2,]
tempresi<-diag(var(tempresidual))
resi<-matrix(0,length(tempresi),length(tempresi))
diag(resi)<-tempresi
risk<-t(w)%*%(t(x)%*%covf%*%x+resi)%*%w
return(sqrt(risk))
}#Get the risk of porto in d2, d1 is the day start to calculate risk

```
